### 2013-03-28 doc/sosp13/evaluation.tex
minor edits
eval in progres

\paragraph{Putting it all together with Unbalanced Tree Search in memory
(UTS).} Figure~\ref{fig:grappa-uts} shows the overall performance of \Grappa
running UTS. The point of this experiment is to demonstrate whether \Grappa's
context switching and communication layers can in fact be used together, while
balancing workload, to run an irregular application efficiently. We look at two classes of trees, T1 and T3, from the original benchmark. T1
trees are very shallow and wide (i.e., significant parallel slack), while T3
trees are very deep (i.e., little parallel slack). When the access to each
vertex is a random access, the critical path to search T3 trees is very long,
hence the low performance and scalability. On such trees, we do not expect there to be
sufficient concurrency for any system, including \Grappa, to achieve high
throughput --- at the 16-node data point, the average active
tasks per core over the search is 775 and 13 for T1 and T3, respectively. On the other hand \Grappa performs and scales very well for T1 trees.

@@

\subsection{Comparing \Grappa to Other Systems}

@@

\paragraph{Message size and latency.}
Distribution if possible. With and without aggregation.

@@

\paragraph{Frequency of remote requests.}

>>>>

\paragraph{Putting it all together with Unbalanced Tree Search in memory
(UTS).} 
Figure~\ref{fig:grappa-uts} shows the overall performance of \Grappa running
UTS. The point of this experiment is to demonstrate whether \Grappa's context
switching and communication layers can in fact be used together, while
balancing workload, to run an irregular application efficiently. Visiting
vertices in the distributed tree requires mostly remote accesses, and because
each vertex in the tree must be visited before it can be expanded, blocking
remote reads are required. 
In this case, we are forced to context switch to tolerate the remote access and continue aggregating. 
We look at two classes of trees, T1 and T3, from
the original benchmark. T1 trees are very shallow and wide (i.e., significant
parallel slack), while T3 trees are very deep (i.e., little parallel slack).
When the access to each vertex is a random access, the critical path to search
T3 trees is very long, hence the low performance and scalability. On such
trees, we do not expect there to be sufficient concurrency for any system,
including \Grappa, to achieve high throughput --- at the 16-node data point,
the average active tasks per core over the search is 775 and 13 for T1 and T3,
respectively. On the other hand \Grappa performs and scales very well for T1
trees.

@@

\subsection{Comparing \Grappa to Other Systems}
\label{eval:mainperf}

@@

\paragraph{Message size and latency.}

To characterize the effectiveness of aggregation, we collected
histograms of aggregated message sizes and application memory request
latency on BFS and UTS.

Figure \ref{fig:grappa-message-size} shows the distribution of message
sizes we are able to aggregate before aggregation times out and
sends. We see different behavior between UTS and BFS.

In UTS, we obtained the best throughput by flushing frequently: on the order 100 microseconds , but
this mean

In BFS, we see a trimodal distribution. There are two reasons for
this. First, in BFS, we obtained the best throughput by flushing at
least 500 microseconds apart, but also flushing whenever the core went
idle. This leads to a large number of messages that are not

Recall that global memory can be accessed in two ways. For requests of
locations that are expected to shared, delegate operations are
used. For requests of non-shared locations where locality can be
exploited, explicit cache operations are used. We see this reflected
in the fraction of requests that are handled remotely: less than one
percent of delegate operations in both BFS and UTS access local
data. Since explicit cache operations are intended to exploit
locality; they more often access data on the local node. Only 20
percent of UTS explicit cache operations are remote, whereas 44
percent of BFS explict cache operations are remote.

The bimodal nature of the BFS distribution is due to a locality optimization that o

Both

In BFS we exploit a large
 Since we are traversing power-law graphs,
some vertices have a very high number of edges. We exploit locality in
BFS by having tasks visit vertices whose edge lists are stored on the
local node. When this local traversal hits a high-degree vertex, BFS
is able to generate a large number of

Figure \ref{fig:grappa-latency} shows

We see different aggregation behavior between BFS and UTS:

In BFS, the bulk of remote accesses are done to take owner

Conversely, UTS attempts to

Distribution if possible. With and without aggregation.

@@
